\bf Supplementary Material: What is the Best Way to Display Two Time Series to Read Association?

### 2016-02-15 paper/supplementary.Rnw
supp material
touch up

\begin{table}[h]
\centering
\caption{Number of times $n$ selections from a lineup evaluation were made. The subject who made the most plot selections within their ten evaluations is additionally reported. There is no relationship between a subject's demographics and a likelihood to make multiple selections.}
\label{table}
<<tabattempts, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
attempts <- summarise(group_by(full.sub, subj_id, pic_id), attempts = max(attempts))
attempts.table <- data.frame(table(attempts$attempts))
attempts.table$most <- c(0,0,0,5,3,1,1)
colnames(attempts.table) <- c("Selections", "Whole Sample", "Subject 123")
kable(attempts.table, format="latex")
@
\end{table}

@@

\begin{figure}[htbp]
\centering
<<random2, dependson='random', fig.height=6, fig.width=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ability <- merge(full.sub[,c("subj_id", "pic_id", "score", "weights")], bylineup.sub[c("pic_id", "percent")], by="pic_id")
ability <- summarise(group_by(ability, subj_id), actual=sum(score), estimated=sum(percent*weights))
ability$diff <- ability$actual - ability$estimated
ability.re <- merge(ability, randomeffects, by="subj_id")
ggplot(data=ability.re, aes(x=diff, y=re)) + geom_point() + labs(x="Visual Ability", y="Random Effects")
@
\caption{Visual ability plotted against random effects. The diagonal pattern suggests a strong positive relationship, indicating that the random effects in the model are a suitable measure of visual ability.}
\label{random2}
\end{figure}

>>>>

\begin{table}[h]
\centering
\caption{Number of times $n$ selections were made in a lineup evaluation. The subject who made the most plot selections within their ten evaluations is additionally reported. There is no relationship between a subject's demographics and a likelihood to make multiple selections.}
\label{table}
<<tabattempts, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
attempts <- summarise(group_by(full.sub, subj_id, pic_id), attempts = max(attempts))
attempts.table <- data.frame(table(attempts$attempts))
attempts.table$most <- c(0,0,0,5,3,1,1)
colnames(attempts.table) <- c("Selections", "Whole Sample", "Subject 123")
kable(attempts.table, format="latex")
@
\end{table}

@@

\begin{figure}[htbp]
\centering
<<random2, dependson='random', fig.height=6, fig.width=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ability <- merge(full.sub[,c("subj_id", "pic_id", "score", "weights")], bylineup.sub[c("pic_id", "percent")], by="pic_id")
ability <- summarise(group_by(ability, subj_id), actual=sum(score), estimated=sum(percent*weights))
ability$diff <- ability$actual - ability$estimated
ability.re <- merge(ability, randomeffects, by="subj_id")
ggplot(data=ability.re, aes(x=diff, y=re)) + geom_point() + labs(x="Visual Ability", y="Random Effects")
@
\caption{Visual ability plotted against random effects. The diagonal pattern suggests a strong positive relationship, indicating that the random effects in the model suitably measure visual ability.}
\label{random2}
\end{figure}
